Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add clarity by labeling hypotheses

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative 
events supports our hypothesis that event salience is coupled with online 
social cohesion. The frequency of all and negative events are thus associated 
with greater shared trajectories with social cohesion that would be expected 
by chance. However, when we specifically target positive events, the connection
to social cohesion fades, providing further support for our hypothesis. 
Positive events may be less coupled to social cohesion than more salient 
negative events during times of turmoil; by contrast, overall event frequency 
and negative event frequency are coupled with Twitter social cohesion.

>>>>

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative 
events supports our first hypothesis that event salience is coupled with online 
social cohesion. The frequency of all and negative events are thus associated 
with greater shared trajectories with social cohesion that would be expected 
by chance. However, when we specifically target positive events, the connection
to social cohesion fades, providing further support for our second hypothesis. 
Positive events may be less coupled to social cohesion than more salient 
negative events during times of turmoil; by contrast, overall event frequency 
and negative event frequency are coupled with Twitter social cohesion.
